---
title: "系列位置効果"
author: '@kohske'
output:
  html_document:
    mathjax: null
    highlight: null
    theme: null
    css: ../lib/jspsych-6.1.0/css/jspsych.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r}
library(htmltools)
tagList(
  tags$script(src='../lib/jspsych-6.1.0/jspsych.js'),
  tags$script(src='../lib/jspsych-6.1.0/plugins/jspsych-html-keyboard-response.js'),
  tags$script(src='../lib/jspsych-psychophysics-0.3/jspsych-psychophysics.js')
)
```

<script>
var rep_item_min = 3;
var rep_item_max = 10;
var n_conditions = 6;

var stim_list = [
  [0,"1. かな2文字_短提示",0.25,"やま"  ],
  [0,"1. かな2文字_短提示",0.25,"くし"  ],
  [0,"1. かな2文字_短提示",0.25,"えび"  ],
  [0,"1. かな2文字_短提示",0.25,"ねぎ"  ],
  [0,"1. かな2文字_短提示",0.25,"すな"  ],
  [0,"1. かな2文字_短提示",0.25,"こま"  ],
  [0,"1. かな2文字_短提示",0.25,"のど"  ],
  [0,"1. かな2文字_短提示",0.25,"こや"  ],
  [0,"1. かな2文字_短提示",0.25,"ふた"  ],
  [0,"1. かな2文字_短提示",0.25,"そら"  ],
  [0,"1. かな2文字_短提示",0.25,"あお"  ],
  [0,"1. かな2文字_短提示",0.25,"なべ"  ],
  [0,"1. かな2文字_短提示",0.25,"かげ"  ],
  [0,"1. かな2文字_短提示",0.25,"むね"  ],
  [0,"1. かな2文字_短提示",0.25,"はら"  ],
  [0,"1. かな2文字_短提示",0.25,"おか"  ],
  [0,"1. かな2文字_短提示",0.25,"ゆび"  ],
  [0,"1. かな2文字_短提示",0.25,"くい"  ],
  [0,"1. かな2文字_短提示",0.25,"たけ"  ],
  [0,"1. かな2文字_短提示",0.25,"はし"  ],
  [0,"1. かな2文字_短提示",0.25,"うま"  ],
  [0,"1. かな2文字_短提示",0.25,"しろ"  ],
  [0,"1. かな2文字_短提示",0.25,"たま"  ],
  [0,"1. かな2文字_短提示",0.25,"あき"  ],
  [0,"1. かな2文字_短提示",0.25,"はる"  ],
  [0,"1. かな2文字_短提示",0.25,"くわ"  ],
  [0,"1. かな2文字_短提示",0.25,"ひま"  ],
  [0,"1. かな2文字_短提示",0.25,"やり"  ],
  [0,"1. かな2文字_短提示",0.25,"こけ"  ],
  [0,"1. かな2文字_短提示",0.25,"くま"  ],
  [0,"1. かな2文字_短提示",0.25,"ひる"  ],
  [0,"1. かな2文字_短提示",0.25,"はち"  ],
  [0,"1. かな2文字_短提示",0.25,"むら"  ],
  [0,"1. かな2文字_短提示",0.25,"ほね"  ],
  [0,"1. かな2文字_短提示",0.25,"こい"  ],
  [0,"1. かな2文字_短提示",0.25,"たな"  ],
  [0,"1. かな2文字_短提示",0.25,"はだ"  ],
  [0,"1. かな2文字_短提示",0.25,"つえ"  ],
  [0,"1. かな2文字_短提示",0.25,"へび"  ],
  [0,"1. かな2文字_短提示",0.25,"ふえ"  ],
  [0,"1. かな2文字_短提示",0.25,"きち"  ],
  [0,"1. かな2文字_短提示",0.25,"もり"  ],
  [0,"1. かな2文字_短提示",0.25,"どう"  ],
  [0,"1. かな2文字_短提示",0.25,"ろく"  ],
  [0,"1. かな2文字_短提示",0.25,"おば"  ],
  [0,"1. かな2文字_短提示",0.25,"ふね"  ],
  [0,"1. かな2文字_短提示",0.25,"いけ"  ],
  [0,"1. かな2文字_短提示",0.25,"たび"  ],
  [0,"1. かな2文字_短提示",0.25,"ゆみ"  ],
  [0,"1. かな2文字_短提示",0.25,"てら"  ],
  [0,"1. かな2文字_短提示",0.25,"かめ"  ],
  [0,"1. かな2文字_短提示",0.25,"ゆり"  ],
  [1,"2. かな2文字_長提示",0.5,"かわ"  ],
  [1,"2. かな2文字_長提示",0.5,"ちり"  ],
  [1,"2. かな2文字_長提示",0.5,"たこ"  ],
  [1,"2. かな2文字_長提示",0.5,"いも"  ],
  [1,"2. かな2文字_長提示",0.5,"つち"  ],
  [1,"2. かな2文字_長提示",0.5,"いた"  ],
  [1,"2. かな2文字_長提示",0.5,"くび"  ],
  [1,"2. かな2文字_長提示",0.5,"いえ"  ],
  [1,"2. かな2文字_長提示",0.5,"そこ"  ],
  [1,"2. かな2文字_長提示",0.5,"うみ"  ],
  [1,"2. かな2文字_長提示",0.5,"くろ"  ],
  [1,"2. かな2文字_長提示",0.5,"はい"  ],
  [1,"2. かな2文字_長提示",0.5,"ふち"  ],
  [1,"2. かな2文字_長提示",0.5,"りす"  ],
  [1,"2. かな2文字_長提示",0.5,"うで"  ],
  [1,"2. かな2文字_長提示",0.5,"たに"  ],
  [1,"2. かな2文字_長提示",0.5,"はな"  ],
  [1,"2. かな2文字_長提示",0.5,"くら"  ],
  [1,"2. かな2文字_長提示",0.5,"しま"  ],
  [1,"2. かな2文字_長提示",0.5,"さら"  ],
  [1,"2. かな2文字_長提示",0.5,"しか"  ],
  [1,"2. かな2文字_長提示",0.5,"あか"  ],
  [1,"2. かな2文字_長提示",0.5,"みき"  ],
  [1,"2. かな2文字_長提示",0.5,"ふゆ"  ],
  [1,"2. かな2文字_長提示",0.5,"なつ"  ],
  [1,"2. かな2文字_長提示",0.5,"かね"  ],
  [1,"2. かな2文字_長提示",0.5,"ねつ"  ],
  [1,"2. かな2文字_長提示",0.5,"とげ"  ],
  [1,"2. かな2文字_長提示",0.5,"いね"  ],
  [1,"2. かな2文字_長提示",0.5,"さる"  ],
  [1,"2. かな2文字_長提示",0.5,"よる"  ],
  [1,"2. かな2文字_長提示",0.5,"くも"  ],
  [1,"2. かな2文字_長提示",0.5,"まち"  ],
  [1,"2. かな2文字_長提示",0.5,"いし"  ],
  [1,"2. かな2文字_長提示",0.5,"ふな"  ],
  [1,"2. かな2文字_長提示",0.5,"かさ"  ],
  [1,"2. かな2文字_長提示",0.5,"もち"  ],
  [1,"2. かな2文字_長提示",0.5,"あし"  ],
  [1,"2. かな2文字_長提示",0.5,"しだ"  ],
  [1,"2. かな2文字_長提示",0.5,"るす"  ],
  [1,"2. かな2文字_長提示",0.5,"はか"  ],
  [1,"2. かな2文字_長提示",0.5,"そば"  ],
  [1,"2. かな2文字_長提示",0.5,"てつ"  ],
  [1,"2. かな2文字_長提示",0.5,"よん"  ],
  [1,"2. かな2文字_長提示",0.5,"おじ"  ],
  [1,"2. かな2文字_長提示",0.5,"とり"  ],
  [1,"2. かな2文字_長提示",0.5,"ひめ"  ],
  [1,"2. かな2文字_長提示",0.5,"おと"  ],
  [1,"2. かな2文字_長提示",0.5,"ゆか"  ],
  [1,"2. かな2文字_長提示",0.5,"つる"  ],
  [1,"2. かな2文字_長提示",0.5,"かも"  ],
  [1,"2. かな2文字_長提示",0.5,"うり"  ],
  [2,"3. 漢字2文字_短提示",0.25,"愛情"  ],
  [2,"3. 漢字2文字_短提示",0.25,"腕前"  ],
  [2,"3. 漢字2文字_短提示",0.25,"遠足"  ],
  [2,"3. 漢字2文字_短提示",0.25,"縁談"  ],
  [2,"3. 漢字2文字_短提示",0.25,"音楽"  ],
  [2,"3. 漢字2文字_短提示",0.25,"海岸"  ],
  [2,"3. 漢字2文字_短提示",0.25,"怪物"  ],
  [2,"3. 漢字2文字_短提示",0.25,"片隅"  ],
  [2,"3. 漢字2文字_短提示",0.25,"学校"  ],
  [2,"3. 漢字2文字_短提示",0.25,"外国"  ],
  [2,"3. 漢字2文字_短提示",0.25,"歓声"  ],
  [2,"3. 漢字2文字_短提示",0.25,"休日"  ],
  [2,"3. 漢字2文字_短提示",0.25,"業績"  ],
  [2,"3. 漢字2文字_短提示",0.25,"教養"  ],
  [2,"3. 漢字2文字_短提示",0.25,"暗闇"  ],
  [2,"3. 漢字2文字_短提示",0.25,"決着"  ],
  [2,"3. 漢字2文字_短提示",0.25,"現象"  ],
  [2,"3. 漢字2文字_短提示",0.25,"建築"  ],
  [2,"3. 漢字2文字_短提示",0.25,"光景"  ],
  [2,"3. 漢字2文字_短提示",0.25,"効率"  ],
  [2,"3. 漢字2文字_短提示",0.25,"黒板"  ],
  [2,"3. 漢字2文字_短提示",0.25,"再現"  ],
  [2,"3. 漢字2文字_短提示",0.25,"質問"  ],
  [2,"3. 漢字2文字_短提示",0.25,"弱点"  ],
  [2,"3. 漢字2文字_短提示",0.25,"宿題"  ],
  [2,"3. 漢字2文字_短提示",0.25,"出発"  ],
  [2,"3. 漢字2文字_短提示",0.25,"生涯"  ],
  [2,"3. 漢字2文字_短提示",0.25,"少年"  ],
  [2,"3. 漢字2文字_短提示",0.25,"心臓"  ],
  [2,"3. 漢字2文字_短提示",0.25,"新聞"  ],
  [2,"3. 漢字2文字_短提示",0.25,"静寂"  ],
  [2,"3. 漢字2文字_短提示",0.25,"青春"  ],
  [2,"3. 漢字2文字_短提示",0.25,"生命"  ],
  [2,"3. 漢字2文字_短提示",0.25,"選択"  ],
  [2,"3. 漢字2文字_短提示",0.25,"相談"  ],
  [2,"3. 漢字2文字_短提示",0.25,"側面"  ],
  [2,"3. 漢字2文字_短提示",0.25,"脱線"  ],
  [2,"3. 漢字2文字_短提示",0.25,"担当"  ],
  [2,"3. 漢字2文字_短提示",0.25,"断片"  ],
  [2,"3. 漢字2文字_短提示",0.25,"電灯"  ],
  [2,"3. 漢字2文字_短提示",0.25,"統計"  ],
  [2,"3. 漢字2文字_短提示",0.25,"独学"  ],
  [2,"3. 漢字2文字_短提示",0.25,"爆音"  ],
  [2,"3. 漢字2文字_短提示",0.25,"発展"  ],
  [2,"3. 漢字2文字_短提示",0.25,"発明"  ],
  [2,"3. 漢字2文字_短提示",0.25,"反省"  ],
  [2,"3. 漢字2文字_短提示",0.25,"人柄"  ],
  [2,"3. 漢字2文字_短提示",0.25,"病室"  ],
  [2,"3. 漢字2文字_短提示",0.25,"防衛"  ],
  [2,"3. 漢字2文字_短提示",0.25,"凡人"  ],
  [2,"3. 漢字2文字_短提示",0.25,"密着"  ],
  [2,"3. 漢字2文字_短提示",0.25,"領域"  ],
  [3,"4. 漢字2文字_長提示",0.5,"足音"  ],
  [3,"4. 漢字2文字_長提示",0.5,"安心"  ],
  [3,"4. 漢字2文字_長提示",0.5,"演劇"  ],
  [3,"4. 漢字2文字_長提示",0.5,"鉛筆"  ],
  [3,"4. 漢字2文字_長提示",0.5,"円満"  ],
  [3,"4. 漢字2文字_長提示",0.5,"海草"  ],
  [3,"4. 漢字2文字_長提示",0.5,"学者"  ],
  [3,"4. 漢字2文字_長提示",0.5,"革新"  ],
  [3,"4. 漢字2文字_長提示",0.5,"活力"  ],
  [3,"4. 漢字2文字_長提示",0.5,"鑑賞"  ],
  [3,"4. 漢字2文字_長提示",0.5,"簡単"  ],
  [3,"4. 漢字2文字_長提示",0.5,"教室"  ],
  [3,"4. 漢字2文字_長提示",0.5,"驚嘆"  ],
  [3,"4. 漢字2文字_長提示",0.5,"緊張"  ],
  [3,"4. 漢字2文字_長提示",0.5,"空想"  ],
  [3,"4. 漢字2文字_長提示",0.5,"経営"  ],
  [3,"4. 漢字2文字_長提示",0.5,"感激"  ],
  [3,"4. 漢字2文字_長提示",0.5,"幻滅"  ],
  [3,"4. 漢字2文字_長提示",0.5,"講演"  ],
  [3,"4. 漢字2文字_長提示",0.5,"幸福"  ],
  [3,"4. 漢字2文字_長提示",0.5,"国境"  ],
  [3,"4. 漢字2文字_長提示",0.5,"作品"  ],
  [3,"4. 漢字2文字_長提示",0.5,"品物"  ],
  [3,"4. 漢字2文字_長提示",0.5,"収入"  ],
  [3,"4. 漢字2文字_長提示",0.5,"出血"  ],
  [3,"4. 漢字2文字_長提示",0.5,"小説"  ],
  [3,"4. 漢字2文字_長提示",0.5,"招待"  ],
  [3,"4. 漢字2文字_長提示",0.5,"消滅"  ],
  [3,"4. 漢字2文字_長提示",0.5,"真実"  ],
  [3,"4. 漢字2文字_長提示",0.5,"信用"  ],
  [3,"4. 漢字2文字_長提示",0.5,"生活"  ],
  [3,"4. 漢字2文字_長提示",0.5,"推定"  ],
  [3,"4. 漢字2文字_長提示",0.5,"聖書"  ],
  [3,"4. 漢字2文字_長提示",0.5,"西洋"  ],
  [3,"4. 漢字2文字_長提示",0.5,"先輩"  ],
  [3,"4. 漢字2文字_長提示",0.5,"体験"  ],
  [3,"4. 漢字2文字_長提示",0.5,"大衆"  ],
  [3,"4. 漢字2文字_長提示",0.5,"旅人"  ],
  [3,"4. 漢字2文字_長提示",0.5,"徹底"  ],
  [3,"4. 漢字2文字_長提示",0.5,"天井"  ],
  [3,"4. 漢字2文字_長提示",0.5,"同調"  ],
  [3,"4. 漢字2文字_長提示",0.5,"農園"  ],
  [3,"4. 漢字2文字_長提示",0.5,"俳優"  ],
  [3,"4. 漢字2文字_長提示",0.5,"歯車"  ],
  [3,"4. 漢字2文字_長提示",0.5,"発表"  ],
  [3,"4. 漢字2文字_長提示",0.5,"母親"  ],
  [3,"4. 漢字2文字_長提示",0.5,"人影"  ],
  [3,"4. 漢字2文字_長提示",0.5,"風潮"  ],
  [3,"4. 漢字2文字_長提示",0.5,"複雑"  ],
  [3,"4. 漢字2文字_長提示",0.5,"本心"  ],
  [3,"4. 漢字2文字_長提示",0.5,"横顔"  ],
  [3,"4. 漢字2文字_長提示",0.5,"冷酷"  ],
  [4,"5. かな1文字_短提示",0.25,"あ"  ],
  [4,"5. かな1文字_短提示",0.25,"い"  ],
  [4,"5. かな1文字_短提示",0.25,"う"  ],
  [4,"5. かな1文字_短提示",0.25,"え"  ],
  [4,"5. かな1文字_短提示",0.25,"お"  ],
  [4,"5. かな1文字_短提示",0.25,"か"  ],
  [4,"5. かな1文字_短提示",0.25,"き"  ],
  [4,"5. かな1文字_短提示",0.25,"く"  ],
  [4,"5. かな1文字_短提示",0.25,"け"  ],
  [4,"5. かな1文字_短提示",0.25,"こ"  ],
  [4,"5. かな1文字_短提示",0.25,"さ"  ],
  [4,"5. かな1文字_短提示",0.25,"し"  ],
  [4,"5. かな1文字_短提示",0.25,"す"  ],
  [4,"5. かな1文字_短提示",0.25,"せ"  ],
  [4,"5. かな1文字_短提示",0.25,"そ"  ],
  [4,"5. かな1文字_短提示",0.25,"た"  ],
  [4,"5. かな1文字_短提示",0.25,"ち"  ],
  [4,"5. かな1文字_短提示",0.25,"つ"  ],
  [4,"5. かな1文字_短提示",0.25,"て"  ],
  [4,"5. かな1文字_短提示",0.25,"と"  ],
  [4,"5. かな1文字_短提示",0.25,"な"  ],
  [4,"5. かな1文字_短提示",0.25,"に"  ],
  [4,"5. かな1文字_短提示",0.25,"ぬ"  ],
  [4,"5. かな1文字_短提示",0.25,"ね"  ],
  [4,"5. かな1文字_短提示",0.25,"の"  ],
  [4,"5. かな1文字_短提示",0.25,"は"  ],
  [4,"5. かな1文字_短提示",0.25,"ひ"  ],
  [4,"5. かな1文字_短提示",0.25,"ふ"  ],
  [4,"5. かな1文字_短提示",0.25,"へ"  ],
  [4,"5. かな1文字_短提示",0.25,"ほ"  ],
  [4,"5. かな1文字_短提示",0.25,"ま"  ],
  [4,"5. かな1文字_短提示",0.25,"み"  ],
  [4,"5. かな1文字_短提示",0.25,"む"  ],
  [4,"5. かな1文字_短提示",0.25,"め"  ],
  [4,"5. かな1文字_短提示",0.25,"も"  ],
  [4,"5. かな1文字_短提示",0.25,"や"  ],
  [4,"5. かな1文字_短提示",0.25,"ゆ"  ],
  [4,"5. かな1文字_短提示",0.25,"よ"  ],
  [4,"5. かな1文字_短提示",0.25,"わ"  ],
  [4,"5. かな1文字_短提示",0.25,"あ"  ],
  [4,"5. かな1文字_短提示",0.25,"い"  ],
  [4,"5. かな1文字_短提示",0.25,"う"  ],
  [4,"5. かな1文字_短提示",0.25,"え"  ],
  [4,"5. かな1文字_短提示",0.25,"お"  ],
  [4,"5. かな1文字_短提示",0.25,"か"  ],
  [4,"5. かな1文字_短提示",0.25,"き"  ],
  [4,"5. かな1文字_短提示",0.25,"く"  ],
  [4,"5. かな1文字_短提示",0.25,"け"  ],
  [4,"5. かな1文字_短提示",0.25,"こ"  ],
  [4,"5. かな1文字_短提示",0.25,"さ"  ],
  [4,"5. かな1文字_短提示",0.25,"し"  ],
  [4,"5. かな1文字_短提示",0.25,"す"  ],
  [5,"6. かな1文字_長提示",0.5,"あ"  ],
  [5,"6. かな1文字_長提示",0.5,"い"  ],
  [5,"6. かな1文字_長提示",0.5,"う"  ],
  [5,"6. かな1文字_長提示",0.5,"え"  ],
  [5,"6. かな1文字_長提示",0.5,"お"  ],
  [5,"6. かな1文字_長提示",0.5,"か"  ],
  [5,"6. かな1文字_長提示",0.5,"き"  ],
  [5,"6. かな1文字_長提示",0.5,"く"  ],
  [5,"6. かな1文字_長提示",0.5,"け"  ],
  [5,"6. かな1文字_長提示",0.5,"こ"  ],
  [5,"6. かな1文字_長提示",0.5,"さ"  ],
  [5,"6. かな1文字_長提示",0.5,"し"  ],
  [5,"6. かな1文字_長提示",0.5,"す"  ],
  [5,"6. かな1文字_長提示",0.5,"せ"  ],
  [5,"6. かな1文字_長提示",0.5,"そ"  ],
  [5,"6. かな1文字_長提示",0.5,"た"  ],
  [5,"6. かな1文字_長提示",0.5,"ち"  ],
  [5,"6. かな1文字_長提示",0.5,"つ"  ],
  [5,"6. かな1文字_長提示",0.5,"て"  ],
  [5,"6. かな1文字_長提示",0.5,"と"  ],
  [5,"6. かな1文字_長提示",0.5,"な"  ],
  [5,"6. かな1文字_長提示",0.5,"に"  ],
  [5,"6. かな1文字_長提示",0.5,"ぬ"  ],
  [5,"6. かな1文字_長提示",0.5,"ね"  ],
  [5,"6. かな1文字_長提示",0.5,"の"  ],
  [5,"6. かな1文字_長提示",0.5,"は"  ],
  [5,"6. かな1文字_長提示",0.5,"ひ"  ],
  [5,"6. かな1文字_長提示",0.5,"ふ"  ],
  [5,"6. かな1文字_長提示",0.5,"へ"  ],
  [5,"6. かな1文字_長提示",0.5,"ほ"  ],
  [5,"6. かな1文字_長提示",0.5,"ま"  ],
  [5,"6. かな1文字_長提示",0.5,"み"  ],
  [5,"6. かな1文字_長提示",0.5,"む"  ],
  [5,"6. かな1文字_長提示",0.5,"め"  ],
  [5,"6. かな1文字_長提示",0.5,"も"  ],
  [5,"6. かな1文字_長提示",0.5,"や"  ],
  [5,"6. かな1文字_長提示",0.5,"ゆ"  ],
  [5,"6. かな1文字_長提示",0.5,"よ"  ],
  [5,"6. かな1文字_長提示",0.5,"わ"  ],
  [5,"6. かな1文字_長提示",0.5,"せ"  ],
  [5,"6. かな1文字_長提示",0.5,"そ"  ],
  [5,"6. かな1文字_長提示",0.5,"た"  ],
  [5,"6. かな1文字_長提示",0.5,"ち"  ],
  [5,"6. かな1文字_長提示",0.5,"つ"  ],
  [5,"6. かな1文字_長提示",0.5,"て"  ],
  [5,"6. かな1文字_長提示",0.5,"と"  ],
  [5,"6. かな1文字_長提示",0.5,"な"  ],
  [5,"6. かな1文字_長提示",0.5,"に"  ],
  [5,"6. かな1文字_長提示",0.5,"ぬ"  ],
  [5,"6. かな1文字_長提示",0.5,"ね"  ],
  [5,"6. かな1文字_長提示",0.5,"の"  ],
  [5,"6. かな1文字_長提示",0.5,"ま"  ]
];
</script>

```{r}
tagList(tags$script(src='main.js'))
```


