---
title: "系列位置効果"
author: '@kohske'
output:
  html_document:
    mathjax: null
    highlight: null
    theme: null
    css: ../lib/jspsych-6.1.0/css/jspsych.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r}
library(htmltools)
tagList(
  tags$script(src='../lib/jspsych-6.1.0/jspsych.js'),
  tags$script(src='../lib/jspsych-6.1.0/plugins/jspsych-html-keyboard-response.js'),
  tags$script(src='../lib/jspsych-psychophysics-0.3/jspsych-psychophysics.js')
)
```

<script>
var rep_item_min = 3;
var rep_item_max = 10;
var n_conditions = 6;

var stim_list = [
  [0,"1. かな2文字_短提示",0.75,"やま"  ],
  [0,"1. かな2文字_短提示",0.75,"くし"  ],
  [0,"1. かな2文字_短提示",0.75,"えび"  ],
  [0,"1. かな2文字_短提示",0.75,"ねぎ"  ],
  [0,"1. かな2文字_短提示",0.75,"すな"  ],
  [0,"1. かな2文字_短提示",0.75,"こま"  ],
  [0,"1. かな2文字_短提示",0.75,"のど"  ],
  [0,"1. かな2文字_短提示",0.75,"こや"  ],
  [0,"1. かな2文字_短提示",0.75,"ふた"  ],
  [0,"1. かな2文字_短提示",0.75,"そら"  ],
  [0,"1. かな2文字_短提示",0.75,"あお"  ],
  [0,"1. かな2文字_短提示",0.75,"なべ"  ],
  [0,"1. かな2文字_短提示",0.75,"かげ"  ],
  [0,"1. かな2文字_短提示",0.75,"むね"  ],
  [0,"1. かな2文字_短提示",0.75,"はら"  ],
  [0,"1. かな2文字_短提示",0.75,"おか"  ],
  [0,"1. かな2文字_短提示",0.75,"ゆび"  ],
  [0,"1. かな2文字_短提示",0.75,"くい"  ],
  [0,"1. かな2文字_短提示",0.75,"たけ"  ],
  [0,"1. かな2文字_短提示",0.75,"はし"  ],
  [0,"1. かな2文字_短提示",0.75,"うま"  ],
  [0,"1. かな2文字_短提示",0.75,"しろ"  ],
  [0,"1. かな2文字_短提示",0.75,"たま"  ],
  [0,"1. かな2文字_短提示",0.75,"あき"  ],
  [0,"1. かな2文字_短提示",0.75,"はる"  ],
  [0,"1. かな2文字_短提示",0.75,"くわ"  ],
  [0,"1. かな2文字_短提示",0.75,"ひま"  ],
  [0,"1. かな2文字_短提示",0.75,"やり"  ],
  [0,"1. かな2文字_短提示",0.75,"こけ"  ],
  [0,"1. かな2文字_短提示",0.75,"くま"  ],
  [0,"1. かな2文字_短提示",0.75,"ひる"  ],
  [0,"1. かな2文字_短提示",0.75,"はち"  ],
  [0,"1. かな2文字_短提示",0.75,"むら"  ],
  [0,"1. かな2文字_短提示",0.75,"ほね"  ],
  [0,"1. かな2文字_短提示",0.75,"こい"  ],
  [0,"1. かな2文字_短提示",0.75,"たな"  ],
  [0,"1. かな2文字_短提示",0.75,"はだ"  ],
  [0,"1. かな2文字_短提示",0.75,"つえ"  ],
  [0,"1. かな2文字_短提示",0.75,"へび"  ],
  [0,"1. かな2文字_短提示",0.75,"ふえ"  ],
  [0,"1. かな2文字_短提示",0.75,"きち"  ],
  [0,"1. かな2文字_短提示",0.75,"もり"  ],
  [0,"1. かな2文字_短提示",0.75,"どう"  ],
  [0,"1. かな2文字_短提示",0.75,"ろく"  ],
  [0,"1. かな2文字_短提示",0.75,"おば"  ],
  [0,"1. かな2文字_短提示",0.75,"ふね"  ],
  [0,"1. かな2文字_短提示",0.75,"いけ"  ],
  [0,"1. かな2文字_短提示",0.75,"たび"  ],
  [0,"1. かな2文字_短提示",0.75,"ゆみ"  ],
  [0,"1. かな2文字_短提示",0.75,"てら"  ],
  [0,"1. かな2文字_短提示",0.75,"かめ"  ],
  [0,"1. かな2文字_短提示",0.75,"ゆり"  ],
  [1,"2. かな2文字_長提示",3,"かわ"  ],
  [1,"2. かな2文字_長提示",3,"ちり"  ],
  [1,"2. かな2文字_長提示",3,"たこ"  ],
  [1,"2. かな2文字_長提示",3,"いも"  ],
  [1,"2. かな2文字_長提示",3,"つち"  ],
  [1,"2. かな2文字_長提示",3,"いた"  ],
  [1,"2. かな2文字_長提示",3,"くび"  ],
  [1,"2. かな2文字_長提示",3,"いえ"  ],
  [1,"2. かな2文字_長提示",3,"そこ"  ],
  [1,"2. かな2文字_長提示",3,"うみ"  ],
  [1,"2. かな2文字_長提示",3,"くろ"  ],
  [1,"2. かな2文字_長提示",3,"はい"  ],
  [1,"2. かな2文字_長提示",3,"ふち"  ],
  [1,"2. かな2文字_長提示",3,"りす"  ],
  [1,"2. かな2文字_長提示",3,"うで"  ],
  [1,"2. かな2文字_長提示",3,"たに"  ],
  [1,"2. かな2文字_長提示",3,"はな"  ],
  [1,"2. かな2文字_長提示",3,"くら"  ],
  [1,"2. かな2文字_長提示",3,"しま"  ],
  [1,"2. かな2文字_長提示",3,"さら"  ],
  [1,"2. かな2文字_長提示",3,"しか"  ],
  [1,"2. かな2文字_長提示",3,"あか"  ],
  [1,"2. かな2文字_長提示",3,"みき"  ],
  [1,"2. かな2文字_長提示",3,"ふゆ"  ],
  [1,"2. かな2文字_長提示",3,"なつ"  ],
  [1,"2. かな2文字_長提示",3,"かね"  ],
  [1,"2. かな2文字_長提示",3,"ねつ"  ],
  [1,"2. かな2文字_長提示",3,"とげ"  ],
  [1,"2. かな2文字_長提示",3,"いね"  ],
  [1,"2. かな2文字_長提示",3,"さる"  ],
  [1,"2. かな2文字_長提示",3,"よる"  ],
  [1,"2. かな2文字_長提示",3,"くも"  ],
  [1,"2. かな2文字_長提示",3,"まち"  ],
  [1,"2. かな2文字_長提示",3,"いし"  ],
  [1,"2. かな2文字_長提示",3,"ふな"  ],
  [1,"2. かな2文字_長提示",3,"かさ"  ],
  [1,"2. かな2文字_長提示",3,"もち"  ],
  [1,"2. かな2文字_長提示",3,"あし"  ],
  [1,"2. かな2文字_長提示",3,"しだ"  ],
  [1,"2. かな2文字_長提示",3,"るす"  ],
  [1,"2. かな2文字_長提示",3,"はか"  ],
  [1,"2. かな2文字_長提示",3,"そば"  ],
  [1,"2. かな2文字_長提示",3,"てつ"  ],
  [1,"2. かな2文字_長提示",3,"よん"  ],
  [1,"2. かな2文字_長提示",3,"おじ"  ],
  [1,"2. かな2文字_長提示",3,"とり"  ],
  [1,"2. かな2文字_長提示",3,"ひめ"  ],
  [1,"2. かな2文字_長提示",3,"おと"  ],
  [1,"2. かな2文字_長提示",3,"ゆか"  ],
  [1,"2. かな2文字_長提示",3,"つる"  ],
  [1,"2. かな2文字_長提示",3,"かも"  ],
  [1,"2. かな2文字_長提示",3,"うり"  ],
  [2,"3. 漢字2文字_短提示",0.75,"愛情"  ],
  [2,"3. 漢字2文字_短提示",0.75,"腕前"  ],
  [2,"3. 漢字2文字_短提示",0.75,"遠足"  ],
  [2,"3. 漢字2文字_短提示",0.75,"縁談"  ],
  [2,"3. 漢字2文字_短提示",0.75,"音楽"  ],
  [2,"3. 漢字2文字_短提示",0.75,"海岸"  ],
  [2,"3. 漢字2文字_短提示",0.75,"怪物"  ],
  [2,"3. 漢字2文字_短提示",0.75,"片隅"  ],
  [2,"3. 漢字2文字_短提示",0.75,"学校"  ],
  [2,"3. 漢字2文字_短提示",0.75,"外国"  ],
  [2,"3. 漢字2文字_短提示",0.75,"歓声"  ],
  [2,"3. 漢字2文字_短提示",0.75,"休日"  ],
  [2,"3. 漢字2文字_短提示",0.75,"業績"  ],
  [2,"3. 漢字2文字_短提示",0.75,"教養"  ],
  [2,"3. 漢字2文字_短提示",0.75,"暗闇"  ],
  [2,"3. 漢字2文字_短提示",0.75,"決着"  ],
  [2,"3. 漢字2文字_短提示",0.75,"現象"  ],
  [2,"3. 漢字2文字_短提示",0.75,"建築"  ],
  [2,"3. 漢字2文字_短提示",0.75,"光景"  ],
  [2,"3. 漢字2文字_短提示",0.75,"効率"  ],
  [2,"3. 漢字2文字_短提示",0.75,"黒板"  ],
  [2,"3. 漢字2文字_短提示",0.75,"再現"  ],
  [2,"3. 漢字2文字_短提示",0.75,"質問"  ],
  [2,"3. 漢字2文字_短提示",0.75,"弱点"  ],
  [2,"3. 漢字2文字_短提示",0.75,"宿題"  ],
  [2,"3. 漢字2文字_短提示",0.75,"出発"  ],
  [2,"3. 漢字2文字_短提示",0.75,"生涯"  ],
  [2,"3. 漢字2文字_短提示",0.75,"少年"  ],
  [2,"3. 漢字2文字_短提示",0.75,"心臓"  ],
  [2,"3. 漢字2文字_短提示",0.75,"新聞"  ],
  [2,"3. 漢字2文字_短提示",0.75,"静寂"  ],
  [2,"3. 漢字2文字_短提示",0.75,"青春"  ],
  [2,"3. 漢字2文字_短提示",0.75,"生命"  ],
  [2,"3. 漢字2文字_短提示",0.75,"選択"  ],
  [2,"3. 漢字2文字_短提示",0.75,"相談"  ],
  [2,"3. 漢字2文字_短提示",0.75,"側面"  ],
  [2,"3. 漢字2文字_短提示",0.75,"脱線"  ],
  [2,"3. 漢字2文字_短提示",0.75,"担当"  ],
  [2,"3. 漢字2文字_短提示",0.75,"断片"  ],
  [2,"3. 漢字2文字_短提示",0.75,"電灯"  ],
  [2,"3. 漢字2文字_短提示",0.75,"統計"  ],
  [2,"3. 漢字2文字_短提示",0.75,"独学"  ],
  [2,"3. 漢字2文字_短提示",0.75,"爆音"  ],
  [2,"3. 漢字2文字_短提示",0.75,"発展"  ],
  [2,"3. 漢字2文字_短提示",0.75,"発明"  ],
  [2,"3. 漢字2文字_短提示",0.75,"反省"  ],
  [2,"3. 漢字2文字_短提示",0.75,"人柄"  ],
  [2,"3. 漢字2文字_短提示",0.75,"病室"  ],
  [2,"3. 漢字2文字_短提示",0.75,"防衛"  ],
  [2,"3. 漢字2文字_短提示",0.75,"凡人"  ],
  [2,"3. 漢字2文字_短提示",0.75,"密着"  ],
  [2,"3. 漢字2文字_短提示",0.75,"領域"  ],
  [3,"4. 漢字2文字_長提示",3,"足音"  ],
  [3,"4. 漢字2文字_長提示",3,"安心"  ],
  [3,"4. 漢字2文字_長提示",3,"演劇"  ],
  [3,"4. 漢字2文字_長提示",3,"鉛筆"  ],
  [3,"4. 漢字2文字_長提示",3,"円満"  ],
  [3,"4. 漢字2文字_長提示",3,"海草"  ],
  [3,"4. 漢字2文字_長提示",3,"学者"  ],
  [3,"4. 漢字2文字_長提示",3,"革新"  ],
  [3,"4. 漢字2文字_長提示",3,"活力"  ],
  [3,"4. 漢字2文字_長提示",3,"鑑賞"  ],
  [3,"4. 漢字2文字_長提示",3,"簡単"  ],
  [3,"4. 漢字2文字_長提示",3,"教室"  ],
  [3,"4. 漢字2文字_長提示",3,"驚嘆"  ],
  [3,"4. 漢字2文字_長提示",3,"緊張"  ],
  [3,"4. 漢字2文字_長提示",3,"空想"  ],
  [3,"4. 漢字2文字_長提示",3,"経営"  ],
  [3,"4. 漢字2文字_長提示",3,"感激"  ],
  [3,"4. 漢字2文字_長提示",3,"幻滅"  ],
  [3,"4. 漢字2文字_長提示",3,"講演"  ],
  [3,"4. 漢字2文字_長提示",3,"幸福"  ],
  [3,"4. 漢字2文字_長提示",3,"国境"  ],
  [3,"4. 漢字2文字_長提示",3,"作品"  ],
  [3,"4. 漢字2文字_長提示",3,"品物"  ],
  [3,"4. 漢字2文字_長提示",3,"収入"  ],
  [3,"4. 漢字2文字_長提示",3,"出血"  ],
  [3,"4. 漢字2文字_長提示",3,"小説"  ],
  [3,"4. 漢字2文字_長提示",3,"招待"  ],
  [3,"4. 漢字2文字_長提示",3,"消滅"  ],
  [3,"4. 漢字2文字_長提示",3,"真実"  ],
  [3,"4. 漢字2文字_長提示",3,"信用"  ],
  [3,"4. 漢字2文字_長提示",3,"生活"  ],
  [3,"4. 漢字2文字_長提示",3,"推定"  ],
  [3,"4. 漢字2文字_長提示",3,"聖書"  ],
  [3,"4. 漢字2文字_長提示",3,"西洋"  ],
  [3,"4. 漢字2文字_長提示",3,"先輩"  ],
  [3,"4. 漢字2文字_長提示",3,"体験"  ],
  [3,"4. 漢字2文字_長提示",3,"大衆"  ],
  [3,"4. 漢字2文字_長提示",3,"旅人"  ],
  [3,"4. 漢字2文字_長提示",3,"徹底"  ],
  [3,"4. 漢字2文字_長提示",3,"天井"  ],
  [3,"4. 漢字2文字_長提示",3,"同調"  ],
  [3,"4. 漢字2文字_長提示",3,"農園"  ],
  [3,"4. 漢字2文字_長提示",3,"俳優"  ],
  [3,"4. 漢字2文字_長提示",3,"歯車"  ],
  [3,"4. 漢字2文字_長提示",3,"発表"  ],
  [3,"4. 漢字2文字_長提示",3,"母親"  ],
  [3,"4. 漢字2文字_長提示",3,"人影"  ],
  [3,"4. 漢字2文字_長提示",3,"風潮"  ],
  [3,"4. 漢字2文字_長提示",3,"複雑"  ],
  [3,"4. 漢字2文字_長提示",3,"本心"  ],
  [3,"4. 漢字2文字_長提示",3,"横顔"  ],
  [3,"4. 漢字2文字_長提示",3,"冷酷"  ],
  [4,"5. かな1文字_短提示",0.75,"あ"  ],
  [4,"5. かな1文字_短提示",0.75,"い"  ],
  [4,"5. かな1文字_短提示",0.75,"う"  ],
  [4,"5. かな1文字_短提示",0.75,"え"  ],
  [4,"5. かな1文字_短提示",0.75,"お"  ],
  [4,"5. かな1文字_短提示",0.75,"か"  ],
  [4,"5. かな1文字_短提示",0.75,"き"  ],
  [4,"5. かな1文字_短提示",0.75,"く"  ],
  [4,"5. かな1文字_短提示",0.75,"け"  ],
  [4,"5. かな1文字_短提示",0.75,"こ"  ],
  [4,"5. かな1文字_短提示",0.75,"さ"  ],
  [4,"5. かな1文字_短提示",0.75,"し"  ],
  [4,"5. かな1文字_短提示",0.75,"す"  ],
  [4,"5. かな1文字_短提示",0.75,"せ"  ],
  [4,"5. かな1文字_短提示",0.75,"そ"  ],
  [4,"5. かな1文字_短提示",0.75,"た"  ],
  [4,"5. かな1文字_短提示",0.75,"ち"  ],
  [4,"5. かな1文字_短提示",0.75,"つ"  ],
  [4,"5. かな1文字_短提示",0.75,"て"  ],
  [4,"5. かな1文字_短提示",0.75,"と"  ],
  [4,"5. かな1文字_短提示",0.75,"な"  ],
  [4,"5. かな1文字_短提示",0.75,"に"  ],
  [4,"5. かな1文字_短提示",0.75,"ぬ"  ],
  [4,"5. かな1文字_短提示",0.75,"ね"  ],
  [4,"5. かな1文字_短提示",0.75,"の"  ],
  [4,"5. かな1文字_短提示",0.75,"は"  ],
  [4,"5. かな1文字_短提示",0.75,"ひ"  ],
  [4,"5. かな1文字_短提示",0.75,"ふ"  ],
  [4,"5. かな1文字_短提示",0.75,"へ"  ],
  [4,"5. かな1文字_短提示",0.75,"ほ"  ],
  [4,"5. かな1文字_短提示",0.75,"ま"  ],
  [4,"5. かな1文字_短提示",0.75,"み"  ],
  [4,"5. かな1文字_短提示",0.75,"む"  ],
  [4,"5. かな1文字_短提示",0.75,"め"  ],
  [4,"5. かな1文字_短提示",0.75,"も"  ],
  [4,"5. かな1文字_短提示",0.75,"や"  ],
  [4,"5. かな1文字_短提示",0.75,"ゆ"  ],
  [4,"5. かな1文字_短提示",0.75,"よ"  ],
  [4,"5. かな1文字_短提示",0.75,"わ"  ],
  [4,"5. かな1文字_短提示",0.75,"あ"  ],
  [4,"5. かな1文字_短提示",0.75,"い"  ],
  [4,"5. かな1文字_短提示",0.75,"う"  ],
  [4,"5. かな1文字_短提示",0.75,"え"  ],
  [4,"5. かな1文字_短提示",0.75,"お"  ],
  [4,"5. かな1文字_短提示",0.75,"か"  ],
  [4,"5. かな1文字_短提示",0.75,"き"  ],
  [4,"5. かな1文字_短提示",0.75,"く"  ],
  [4,"5. かな1文字_短提示",0.75,"け"  ],
  [4,"5. かな1文字_短提示",0.75,"こ"  ],
  [4,"5. かな1文字_短提示",0.75,"さ"  ],
  [4,"5. かな1文字_短提示",0.75,"し"  ],
  [4,"5. かな1文字_短提示",0.75,"す"  ],
  [5,"6. かな1文字_長提示",3,"あ"  ],
  [5,"6. かな1文字_長提示",3,"い"  ],
  [5,"6. かな1文字_長提示",3,"う"  ],
  [5,"6. かな1文字_長提示",3,"え"  ],
  [5,"6. かな1文字_長提示",3,"お"  ],
  [5,"6. かな1文字_長提示",3,"か"  ],
  [5,"6. かな1文字_長提示",3,"き"  ],
  [5,"6. かな1文字_長提示",3,"く"  ],
  [5,"6. かな1文字_長提示",3,"け"  ],
  [5,"6. かな1文字_長提示",3,"こ"  ],
  [5,"6. かな1文字_長提示",3,"さ"  ],
  [5,"6. かな1文字_長提示",3,"し"  ],
  [5,"6. かな1文字_長提示",3,"す"  ],
  [5,"6. かな1文字_長提示",3,"せ"  ],
  [5,"6. かな1文字_長提示",3,"そ"  ],
  [5,"6. かな1文字_長提示",3,"た"  ],
  [5,"6. かな1文字_長提示",3,"ち"  ],
  [5,"6. かな1文字_長提示",3,"つ"  ],
  [5,"6. かな1文字_長提示",3,"て"  ],
  [5,"6. かな1文字_長提示",3,"と"  ],
  [5,"6. かな1文字_長提示",3,"な"  ],
  [5,"6. かな1文字_長提示",3,"に"  ],
  [5,"6. かな1文字_長提示",3,"ぬ"  ],
  [5,"6. かな1文字_長提示",3,"ね"  ],
  [5,"6. かな1文字_長提示",3,"の"  ],
  [5,"6. かな1文字_長提示",3,"は"  ],
  [5,"6. かな1文字_長提示",3,"ひ"  ],
  [5,"6. かな1文字_長提示",3,"ふ"  ],
  [5,"6. かな1文字_長提示",3,"へ"  ],
  [5,"6. かな1文字_長提示",3,"ほ"  ],
  [5,"6. かな1文字_長提示",3,"ま"  ],
  [5,"6. かな1文字_長提示",3,"み"  ],
  [5,"6. かな1文字_長提示",3,"む"  ],
  [5,"6. かな1文字_長提示",3,"め"  ],
  [5,"6. かな1文字_長提示",3,"も"  ],
  [5,"6. かな1文字_長提示",3,"や"  ],
  [5,"6. かな1文字_長提示",3,"ゆ"  ],
  [5,"6. かな1文字_長提示",3,"よ"  ],
  [5,"6. かな1文字_長提示",3,"わ"  ],
  [5,"6. かな1文字_長提示",3,"せ"  ],
  [5,"6. かな1文字_長提示",3,"そ"  ],
  [5,"6. かな1文字_長提示",3,"た"  ],
  [5,"6. かな1文字_長提示",3,"ち"  ],
  [5,"6. かな1文字_長提示",3,"つ"  ],
  [5,"6. かな1文字_長提示",3,"て"  ],
  [5,"6. かな1文字_長提示",3,"と"  ],
  [5,"6. かな1文字_長提示",3,"な"  ],
  [5,"6. かな1文字_長提示",3,"に"  ],
  [5,"6. かな1文字_長提示",3,"ぬ"  ],
  [5,"6. かな1文字_長提示",3,"ね"  ],
  [5,"6. かな1文字_長提示",3,"の"  ],
  [5,"6. かな1文字_長提示",3,"ま"  ]
];
</script>

```{r}
tagList(tags$script(src='main.js'))
```


