---
title: "系列位置効果"
author: '@kohske'
output:
  html_document:
    mathjax: null
    highlight: null
    theme: null
    css: ../lib/jspsych-6.1.0/css/jspsych.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r}
library(htmltools)
tagList(
  tags$script(src='../lib/jspsych-6.1.0/jspsych.js'),
  tags$script(src='../lib/jspsych-6.1.0/plugins/jspsych-html-keyboard-response.js'),
  tags$script(src='../lib/jspsych-psychophysics-0.3/jspsych-psychophysics.js')
)
```

<script>
var rep_item_min = 2;
var rep_item_max = 3;
var n_conditions = 6;

var stim_list = [
  [0,"1. かな2文字_短提示",0.75,"ほん"  ],
  [0,"1. かな2文字_短提示",0.75,"わに"  ],
  [0,"1. かな2文字_短提示",0.75,"さい"  ],
  [0,"1. かな2文字_短提示",0.75,"めん"  ],
  [0,"1. かな2文字_短提示",0.75,"へそ"  ],
  [1,"2. かな2文字_長提示",3,"みち"  ],
  [1,"2. かな2文字_長提示",3,"つき"  ],
  [1,"2. かな2文字_長提示",3,"ちか"  ],
  [1,"2. かな2文字_長提示",3,"かい"  ],
  [1,"2. かな2文字_長提示",3,"なす"  ],
  [2,"3. 漢字2文字_短提示",0.75,"字体"  ],
  [2,"3. 漢字2文字_短提示",0.75,"乙女"  ],
  [2,"3. 漢字2文字_短提示",0.75,"人形"  ],
  [2,"3. 漢字2文字_短提示",0.75,"外見"  ],
  [2,"3. 漢字2文字_短提示",0.75,"空手"  ],
  [3,"4. 漢字2文字_長提示",3,"元日"  ],
  [3,"4. 漢字2文字_長提示",3,"木材"  ],
  [3,"4. 漢字2文字_長提示",3,"車体"  ],
  [3,"4. 漢字2文字_長提示",3,"国土"  ],
  [3,"4. 漢字2文字_長提示",3,"音色"  ],
  [4,"5. かな1文字_短提示",0.75,"え"  ],
  [4,"5. かな1文字_短提示",0.75,"と"  ],
  [4,"5. かな1文字_短提示",0.75,"し"  ],
  [4,"5. かな1文字_短提示",0.75,"お"  ],
  [4,"5. かな1文字_短提示",0.75,"も"  ],
  [5,"6. かな1文字_長提示",3,"く"  ],
  [5,"6. かな1文字_長提示",3,"さ"  ],
  [5,"6. かな1文字_長提示",3,"て"  ],
  [5,"6. かな1文字_長提示",3,"な"  ],
  [5,"6. かな1文字_長提示",3,"み"  ]
];

</script>

```{r}
tagList(tags$script(src='main.js'))
```


