---
title: "顔の倒立効果"
author: '@kohske'
output:
  html_document:
    mathjax: null
    highlight: null
    theme: null
    css: ../lib/jspsych-6.1.0/css/jspsych.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r}
library(htmltools)
tagList(
  tags$script(src='../lib/jspsych-6.1.0/jspsych.js'),
  tags$script(src='../lib/jspsych-6.1.0/plugins/jspsych-html-keyboard-response.js'),
  tags$script(src='../lib/jspsych-6.1.0/plugins/jspsych-html-button-response.js'),
  tags$script(src='../lib/jspsych-psychophysics-0.3/jspsych-psychophysics.js')
)
```

<script>
var exp_type = "s";

var upfaces_images = ["image00001.jpg", "image00002.jpg", "image00003.jpg", "image00004.jpg", "image00005.jpg", "image00006.jpg", "image00007.jpg", "image00008.jpg", "image00009.jpg", "image00010.jpg", "image00011.jpg", "image00012.jpg", "image00013.jpg", "image00014.jpg", "image00015.jpg", "image00016.jpg", "image00017.jpg", "image00018.jpg", "image00019.jpg", "image00020.jpg", "image00021.jpg", "image00022.jpg", "image00023.jpg", "image00024.jpg", "image00025.jpg", "image00026.jpg", "image00027.jpg", "image00028.jpg", "image00029.jpg", "image00030.jpg", "image00031.jpg", "image00032.jpg", "image00033.jpg", "image00034.jpg", "image00035.jpg", "image00036.jpg", "image00037.jpg", "image00038.jpg", "image00039.jpg", "image00040.jpg", "image00041.jpg", "image00042.jpg", "image00043.jpg", "image00044.jpg", "image00045.jpg", "image00046.jpg", "image00047.jpg", "image00048.jpg"];

var invfaces_images = ["i_image00049.jpg", "i_image00050.jpg", "i_image00051.jpg", "i_image00052.jpg", "i_image00053.jpg", "i_image00054.jpg", "i_image00055.jpg", "i_image00056.jpg", "i_image00057.jpg", "i_image00058.jpg", "i_image00059.jpg", "i_image00060.jpg", "i_image00061.jpg", "i_image00062.jpg", "i_image00063.jpg", "i_image00064.jpg", "i_image00065.jpg", "i_image00066.jpg", "i_image00067.jpg", "i_image00068.jpg", "i_image00069.jpg", "i_image00070.jpg", "i_image00071.jpg", "i_image00072.jpg", "i_image00073.jpg", "i_image00074.jpg", "i_image00075.jpg", "i_image00076.jpg", "i_image00077.jpg", "i_image00078.jpg", "i_image00079.jpg", "i_image00080.jpg", "i_image00081.jpg", "i_image00082.jpg", "i_image00083.jpg", "i_image00084.jpg", "i_image00085.jpg", "i_image00086.jpg", "i_image00087.jpg", "i_image00088.jpg", "i_image00089.jpg", "i_image00090.jpg", "i_image00091.jpg", "i_image00092.jpg", "i_image00093.jpg", "i_image00094.jpg", "i_image00095.jpg", "i_image00096.jpg"];
</script>

```{r}
tagList(
  tags$script(src='main.js')
)
```
